Fractional Types

### 2013-03-25 rc13/frac2.tex
frac2

\documentclass{llncs}
\usepackage{url}
\usepackage{proof}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{comment}

@@

\newcommand{\todo}[1]{\textbf{TODO:} #1}
\newcommand{\jacques}[1]{\textsc{Jacques says:} #1}
\newcommand{\amr}[1]{\textsc{Amr says:} #1}

@@

\begin{document}
\title{Fractional Types}
\author{Roshan P. James$^{1}$ \and Zachary Sparks$^{1}$ \and Jacques Carette$^{2}$ \and Amr Sabry$^{1}$}
\institute{$^{(1)}$~Indiana University \qquad $^{(2)}$~McMaster University}
\maketitle

@@

{\small
\bibliographystyle{splncs03} 
\bibliography{cites}
}
\end{document}

>>>>

\documentclass[preprint]{sigplanconf}
\usepackage{url}
\usepackage{proof}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{multicol}

@@

\newcommand{\todo}[1]{\textbf{TODO:} #1}
\newcommand{\jacques}[1]{\textsc{Jacques says:} #1}
\newcommand{\amr}[1]{\textsc{Amr says:} #1}
\newtheorem{definition}{Definition}

@@

\begin{document}

\conferenceinfo{ICFP '13}{date, City.} 
\copyrightyear{2013}
\copyrightdata{[to be supplied]}

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Fractional Types}
\authorinfo{Jacques Carette \and Amr Sabry}
           {McMaster University \and Indiana University}
           {carette@mcmaster.ca \and sabry@indiana.edu}

\maketitle

@@

\bibliographystyle{abbrvnat}
\bibliography{cites}

\end{document}
